---
title: 'Exercise #2'
author: "Your name"
date: "date of submission"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# more internal settings can go here
# Consider help pages like:
# https://rmarkdown.rstudio.com/lesson-1.html
# https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf

```

### Loaded packages

```{r libraries}
# Load all packages here, consider to mute output of this code chunk
# https://rmarkdown.rstudio.com/lesson-3.html
```

### Preprocessing / R functions

```{r preprocessing_or_functions, message=FALSE, warning=FALSE}
# If data preprocessing is needed, do it here.
# If you have specific functions, placed them here.
# If this code chunk is not needed, delete it.
```

## 1. Quality control procedures (4 QCPs)

```{r, eval = FALSE}
# Load data from Github (then eval = TRUE)
data <- read_...('http://........')
head(data)
```

### 1.1 Measurement range (Plausible values)

```{r qcp1, eval = FALSE}
# code for qcp2 here, e.g.: (set eval = TRUE to activate the code chunk)
data %>%
  mutate(var1 = ...) %>% 
  group_by(var2) %>% 
  mutate(var3 = ...) %>% 
  summarise(var4 = ..., .groups = 'drop') 

qcp2 <- data %>% summarise(...)
```

**Question**: How many data points are outside the measurement range?

**Answer**:

### 1.2 Plausible rate of change

```{r qcp2}
# code for qcp1 here
```

**Question**: Describe shortly how many data points failed during this QCP and discuss whether there is a certain daytime pattern of failure or not?

**Answer**:

### 1.3 Minimum variability (Persistence)

```{r qcp3}
# code for qcp3 here
```

**Task**: Code in this section should analyses the persistance.

### 1.4 Light intensity

```{r qcp4}
# code for qcp4 here
```

**Task**: Discuss shortly how often and when during daytime the QCP4 flags bad data. Elaborate on some reasons for your results.

**Answer**:

## 2. Synthesis

```{r synthesis}
# code for synthesis here
```

**Task**: Present a table or graph to show how many data points fail during the four specific QCPs. Discuss shortly the reasons for failure and compare the different QCPs against each other.

**Answer**:

## 3. Results

### 3.1 Result (Flagging system: 10-minutes-values)

```{r res1}
# code for results here
```

**Task**: At the end of the code section above you should generate one! tibble or data.frame named `qc_df` with all time information, all data points (temperature and lux) and your outcomes of the different QCPs.

### 3.2 Result (Aggregate to hourly series)

```{r res2}
# code for results here
```

**Task**: At the end of the code section above you should generate one! tibble or data.frame named `hobo_hourly` with averaged temperature values per hour or NA values (if the hour is flagged as bad data). See exercise description for more details.

-   First column: YYYY-DD-MM HH:MM:SS

-   Second column: Temperature values (4 digits), NA values possible
