---
title: "Report_part1"
author: "Immanuel Frenzel"
date: "19 1 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library("lubridate")
library("tidyverse")
library("tibbletime")

theme_set(theme_bw() +  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        plot.title = element_text(size=20)))
```

## Hobo location
The describtion of the place the hobo was positioned was descrieb as followed:
"Outdoor, directly at a north window, next building only 5m away, pot. wind effects, minor sunshine"

Some conclusions should be found in the data:
* Due to the window facing north there should be no direkt sunlight hitting the hobo
* The office behind the window could have radiated light at the hobo. This should be visible expecially
 during the early morning and late afternoon hours, when the office is occupied and the sun has already set
* Heat from the building could radiate. This may could shown by the comparision of meteo-station und hobo temperature data.
```{r lightintenisty, echo=FALSE}
#labes lightintenisities
data <- data %>%
  mutate(SIC = case_when(lux < 0 ~ "NA",
                         lux < 10 ~ "night",
                         lux < 500 ~ "sun_rise_or_set",
                         lux < 2000 ~ "overcast_full",
                         lux < 15000 ~ "overcast_light",
                         lux < 20000 ~ "clear_sky_shady",
                         lux < 50000 ~ "sunshine",
                         lux >= 50000 ~ "sunshine_bright"))

ggplot(data, aes(x = SIC)) + geom_bar() + 
  theme_bw() +
  coord_flip()


```
The plot confirms

```{r lightintenisty, echo=FALSE}
#import clean 10 min timeseries
reimport <- read.csv("https://raw.githubusercontent.com/imifrenzel/hyd_data_management/main/10610854.csv")

#proper date format
data <- reimport %>% 
  mutate(dttm = ymd_hm(reimport$dttm))

#labes lightintenisities
datasumlux <- data %>%
  mutate(hour = hour(dttm)) %>% 
  group_by(hour) %>% 
  summarise(lux = mean(lux, na.rm = TRUE))

ggplot(datasumlux, aes(x = hour, y = lux)) + geom_point() 


```
It seems like


